\begin{center}
    \setlength{\parindent}{15mm}
\end{center}
\chapter{Introduction}\label{ch:intro}
%these sections are optional, up-to the author
\section{Motivation}
\par
Blood transfusion is an extremely important process which saves millions of lives. But, the need and an actual number of donations are not currently balanced in Kazakhstan. 
\par
The reason for this may be absence of marketing and advertising of blood donation and no interest from the younger people to donate. Our project does all of the research and provides optimal solution in order to improve current situation in blood donation.
\par
Blood transfusion is an extremely important process which saves millions of lives. But, the need and an actual number of donations are not currently balanced in Kazakhstan. The actual reason for this may be absence of marketing and advertising of blood donation and no interest from the younger people to donate. Our project does all of the research and provides optimal solution in order to improve current situation in blood donation.
\par
According to World Health Organization, in general we need at least 20 blood donations per 1000 people. But in Kazakhstan the number of donations decreases every year and by 2021 we have only 14.7 blood donations. This leads to lack of blood and a lot of problems when we come to solving emergency situations. Decreasing numbers, no interest in population drives to develop strong community of blood donors.

\section{Aims and Objectives}
\par
The main goal is to increase number of donations firstly to a standard of World Health Organization and then even exceed the amount in order to create sustainable social balance in donation.
\par
By developing one platform for people to track their donations and receive valuable achievements, this will help attracting people to solving the real problem of current lack of blood in Kazakhstan. The recruitment system and marketing strategies will support the development of the 'Donor project' so that it won't be a one time interest, but a continuous and integrated system.
\par
At the Donor Project, we want prepared donors and in the right amount to come to blood centers every day. But this is a difficult and complex task. We are engaged in the correct donation of blood, that is, we are promoting this cause because we want, first of all, to help those in need of blood. But in order to realize and interest potential donors, we use the free main idea - Privileges. They include healthcare facilities and introduce people to a completely new possibility of receiving expensive medical diagnostic just by a blood donation.
\par
Working with government and private companies of healthcare in our country would have a positive impact on our society in general. Our project will attract new people and will integrate key partners existing.
\par
As a first step it is required to connect locally one city, so then we can scale up our online platform and connect other cities. The system doesn't require a lot of manipulations in order to scale, so the process will be easy and fast-forward if we have needed resources such as access to local healthcare organization's data.

\section{Thesis Outline}
The first chapter is \nameref{ch:intro} chapter. It is this one that you are currently reading. It gives insight into the work done. In Chapter \ref{ch:A} we review design system research and marketing strategies that were developed and used for the project. Chapter \ref{ch:B} is describing the solution to the problem and physical representation of online platform which was developed using popular frameworks and Object Oriented Language. And in \nameref{ch:concl} chapter we review our project as an ecosystem and share the results of the whole development process